*Supplementary Material 1*

### 2022-02-21 ms/si.Rmd
Finally figure out how to change RStudio tabs to spaces
Update MS
Add accessions table

---
title: "*Supplementary Material*"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: default
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "frontiers.csl"]
  bookdown::word_document2:
    pandoc_args: [ "--csl", "frontiers.csl"]
    toc: no
    number_sections: no
    reference_docx: Frontiers_Template_SI.docx
header-includes: 
  - \usepackage{float} # keep figures from floating away
  - \usepackage{booktabs} # need for kable tables
  - \usepackage{colortbl} # need for kable tables
  - \makeatletter\renewcommand*{\fps@figure}{H}\makeatother # keep figures from floating away
  - \usepackage{fancyhdr} # enable header
  - \pagestyle{fancy}  # enable header
  - \fancypagestyle{plain}{\pagestyle{fancy}} # show header on first page
  - \renewcommand{\headrulewidth}{0pt} # delete line beneath header
  - \fancyhead[RE,RO]{Supplementary Material} # add header on right side
  - \fancyhead[LO,LE]{} # suppress automatic section header on left side
  - \cfoot{\thepage} # footer
nocite: |
  @*
editor_options: 
  chunk_output_type: console
params:
  doc_type: manual
---

@@

tar_load(
	c(
		sanger_alignment_tbl,
		sanger_sampling,
		sanger_accessions_selection,
		plastome_tree,
		plastid_tree_dated,
		fossil_calibration_tips,
		ppgi_taxonomy,
		monophy_by_clade),
	store = ftol_cache
)

@@

**`r s_table("fossils")`**.
Fossils used as calibration points for molecular dating (`r result_file(s_table("fossils"), "csv") %>% fs::path_file()`).
"n_fos" is the fossil ID number used in our fossil database (https://github.com/pteridophy/fossils).
"minimum_age" (Ma) is the age used for calibration; "lower" is the lower limit of the oldest stratigraphic age for the fossil; "upper" is the upper limit of the oldest stratigraphic age for the fossil.

>>>>

---
title: "*Supplementary Material 1*"
subtitle: "Tables and Figures"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: default
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "frontiers.csl"]
  bookdown::word_document2:
    pandoc_args: [ "--csl", "frontiers.csl"]
    toc: no
    number_sections: no
    reference_docx: Frontiers_Template_SI.docx
header-includes: 
  - \usepackage{float} # keep figures from floating away
  - \usepackage{booktabs} # need for kable tables
  - \usepackage{colortbl} # need for kable tables
  - \makeatletter\renewcommand*{\fps@figure}{H}\makeatother # keep figures from floating away
  - \usepackage{fancyhdr} # enable header
  - \pagestyle{fancy}  # enable header
  - \fancypagestyle{plain}{\pagestyle{fancy}} # show header on first page
  - \renewcommand{\headrulewidth}{0pt} # delete line beneath header
  - \fancyhead[RE,RO]{Supplementary Material} # add header on right side
  - \fancyhead[LO,LE]{} # suppress automatic section header on left side
  - \setlength{\headheight}{13.6pt}
  - \cfoot{\thepage} # footer
editor_options: 
  chunk_output_type: console
params:
  doc_type: manual
---

@@

tar_load(
  c(
    sanger_alignment_tbl,
    sanger_sampling,
    sanger_accessions_selection,
    plastome_tree,
    plastid_tree_dated,
    fossil_calibration_tips,
    ppgi_taxonomy,
    monophy_by_clade,
    acc_table_long),
  store = ftol_cache
)

@@

**`r s_table("fossils")`**.
Fossils used as calibration points for molecular dating (`r result_file(s_table("fossils"), "csv") %>% fs::path_file()`).
"n_fos" is the fossil ID number used in our fossil database (https://github.com/pteridophy/fossils).
"minimum_age" (Ma) is the age used for calibration; "lower" is the lower limit of the oldest stratigraphic age for the fossil; "upper" is the upper limit of the oldest stratigraphic age for the fossil.
For detailed notes and full references for each fossil, see Appendix S2.

```{r accs-save, eval = params$doc_type == "doc"}
write_csv(acc_table_long, result_file(s_table("accs"), "csv"))
```

**`r s_table("accs")`**.
GenBank accessions used in this study (`r result_file(s_table("accs"), "csv") %>% fs::path_file()`).
"species" is the species name as it appears in the phylogenetic tree.
"seq_len" is the total number of bases excluding missing bases ("?", "N", or "-") and only includes bases belonging to loci used in this study (not the entire accession).
"sci_name" is the scientific name in the Pteridocat taxonomic database.
"ncbi_name" is the scientific name used in the NCBI taxonomic database.
"ncbi_taxid" is the NCBI taxonomy database unique identifier.
"outgroup_status" is "in" for ingroup taxa (ferns) and "out" for outgroup taxa.
